---
title: "PCA Demo"
author: "Caitlin Mothes"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Set up by loading libraries and data sets

```{r eval=FALSE}
install.packages("plotly")
```


```{r}
library(tidyverse)
library(lterdatasampler)
library(plotly)
library(ggfortify)


# load crab data
data("pie_crab")

```

inspect the data

```{r}
pie_crab
```


Look at variable correlations
```{r}
pie_crab %>% 
  select(latitude, air_temp:water_temp_sd) %>% 
  cor()
```


Conduct the PCA test

```{r}
crab_pca <- pie_crab %>% 
  select(latitude, air_temp:water_temp_sd) %>%
  prcomp()
```


Look at variance contributions
```{r}
summary(crab_pca)
```

Look at variable loadings
```{r}
crab_pca$rotation
```

Look at site/observation scores
```{r}
cor(crab_pca$x)
```

Make screeplot of variable contributions
```{r}
screeplot(crab_pca)
```

Make a biplot
```{r}
biplot(crab_pca)
```

Make a ggplot biplot (and make it interactive)
```{r eval=FALSE}
ggplotly(autoplot(crab_pca, loadings = TRUE, loadings.label = TRUE) +
  theme_minimal()) 
```


Add PC axes to pie_crab data

```{r}
pie_crab <- bind_cols(pie_crab, crab_pca$x)
```

Conduct the multiple linear regression
```{r}
model <- lm(size ~ PC1 + PC2 + PC3 + PC4 + PC5, data = pie_crab)
```

```{r}
summary(model)
```

